---
title: "Reproducing Powell et Al. 2017"
author: "Fiona Lightbody"
date: "9/28/2020"
output:
  pdf_document: default
bibliography: Powell.bibtex
---

#Reproducing code from 
#[@RN14] 



#COMPLETED: loaded in data and packages 
```{r setup, include=TRUE}
rm(list=ls())

library(survival)
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```
#package 'survival' was built under R version 3.6.2 and was downloaded in the binary format, not the source version

```{r data_input, include=TRUE}
Collection_data <- read_csv("~/Google Drive/AA Graduate /Data and Software Tools EBIO6660/data/Cephalotes_rohweri_collection_data.csv") 
Field_expt <- read_csv("~/Google Drive/AA Graduate /Data and Software Tools EBIO6660/data/Cephalotes_rohweri_field_expt.csv")

Lab_expt <- read_csv("~/Google Drive/AA Graduate /Data and Software Tools EBIO6660/data/Cephalotes_rohweri_lab_expt.csv")

```
#data was readily available by the author in csv format. So far no metadata or code has been located for this paper. 
### PROGRESS REPORT OCT 17
#STILL WORKING ON IT: Next I will work with the data to generate summarizing graphics and work on the first boxplot which I seek to reproduce. Next I will familiarize myself with the survival package in order to generate the survivorship curve. 

### PROGRESS REPORT OCT 25 
##STUCK: need to understand difference between col character and col double: running the above data into R gets this in response (below), maybe because Powell used solely R (not R Studio) to peform his analysis. Code has not yet been receieved, but contact was made. 

### PROGRESS REPORT NOV 2
#STILL WORKING ON IT: Code does not run independently upon first attempt. I split up the code below into sections differentiated by the author. 

# ---------- FIELD COLLECTION DATA ----------

## READ IN FIELD COLLECTION DATA
c_cavs_sum <- read.csv("/Users/scott/Desktop/Ceph AZ ET Cleaned for Analyses/collection_data-cavity_summary_non_incipient.csv") #Cavity data summarized for all non-inicipient colonies.

raw_cavs <- read.csv("/Users/scott/Desktop/Ceph AZ ET Cleaned for Analyses/collection_data-cavity_data_non_incipient.csv")


## POWELL CODE: POPULATION SOLDIER DEPLOYMNET VARIATION
```{r Population.Soldier.Deployment.Variation}
par(pty="s", bty="l", tcl=-0.2, mgp=c(2.4, 0.6, 0), fin=c(4.0, 4.0))
boxplot(c_cavs_sum$mad_dep, cex.axis=0.8, ylim=c(0,18), las=1, xlab=expression(italic("C. rohweri")~"colonies"), ylab="Variation in soldier deployment\n across cavities (MAD)", whisklty=1, boxlwd=1, boxwex=0.7, medlwd=1, whisklwd=1, outpch=1, outcex=1, outlwd=1)
points(1,mean(c_cavs_sum$mad_dep),pch=4,col="black") #To add a point for the calculated mean

boxplot(c_cavs_sum$mad_dep, plot=FALSE) # Print values used to build the boxplot


par(pty="s", bty="l", tcl=-0.2, mgp=c(2.4, 0.6, 0), fin=c(4.0, 4.0))
boxplot(c_cavs_sum$mad_dep_prop, cex.axis=0.8, ylim=c(0,0.12), las=1, xlab=expression(italic("C. rohweri")~"colonies"), ylab="Variation in prop. soldier deployment\n across cavities (MAD)", whisklty=1, boxlwd=1, boxwex=0.7, medlwd=1, whisklwd=1, outpch=1, outcex=1, outlwd=1)
points(1,mean(c_cavs_sum$mad_dep_prop),pch=4,col="black") #To add a point for the calculated mean

boxplot(c_cavs_sum$mad_dep_prop, plot=FALSE) # Print values used to build the bixplot
```


## POPULATION ENTRANCE-USE
```{r Population.Entrance.Use}
### FOR RAW DATA
par(pty="s", bty="l", tcl=-0.02, mgp=c(2.4, 0.6, 0), fin=c(4.0, 4.0))
boxplot(wild_ents$ent_area, cex.axis=0.8, ylim=c(2,39), las=1, log="y", xaxt="n", yaxt="n", xlab=expression(italic("C. rohweri")~"nests"), ylab="Entrance area (mm²)", whisklty=1, boxlwd=1, boxwex=0.7, medlwd=1, whisklwd=1, outpch=1, outcex=1, outlwd=1)
#points(1,mean(wild_ents$ent_area),pch=4,col="black") #To add a point for the calculated mean
ytemptck <- c(2,3,4,5,6,7,8,9,10,20,30,40)
axis(2, at=ytemptck, tck=-0.02, label=F, lwd=0, lwd.ticks=1)
axis(2, at=c(2,5,10,40), label=c(2,5,10,40), mgp=c(3,0.6,0), lwd=0, cex.axis=0.8, las=1)
summary(wild_ents$ent_area)
#Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
cavities#2.100   3.200   4.850   6.916   7.600  39.700

### FOR HEAD-AREAS DATA
par(pty="s", bty="l", tcl=-0.2, mgp=c(2.4, 0.6, 0), fin=c(4.0, 4.0))
boxplot(wild_ents$rel_area, cex.axis=0.8, ylim=c(0.7,18), log="y", xaxt="n", yaxt="n",las=1, xlab=expression(italic("C. rohweri")~"nests"), ylab="Entrance area (head areas)", whisklty=1, boxlwd=1, boxwex=0.7, medlwd=1, whisklwd=1, outpch=1, outcex=1, outlwd=1)
#points(1,mean(wild_ents$rel_area),pch=4,col="black") #To add a point for the calculated mean
ytemptck <- c(1,2,3,4,5,6,7,8,9,10,20)
axis(2, at=ytemptck, tck=-0.02, label=F, lwd=0, lwd.ticks=1)
axis(2, at=c(1,5,10,20), label=c(1,5,10,20), mgp=c(3,0.6,0), lwd=0, cex.axis=0.8, las=1)
summary(wild_ents$rel_area)
#Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#0.700   1.100   1.700   2.381   2.600  13.700 


## GLOBAL SUMMARY OF SOLDIER AND WORKER NUMBERS ACROSS ALL CAVITIES

summary(raw_cavs$soldiers)
#Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#1.000   3.000   7.000   8.886  13.000  37.000 
  
summary(raw_cavs$workers)
#Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#5.00   24.50   39.00   46.63   55.50  160.00 
   
cav_pop <- raw_cavs$colony_size
summary(cav_pop)
#Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#8.00   31.00   46.00   55.52   66.00  197.00 

summary(raw_cavs$t_brood)
#Min. 1st Qu.  Median    Mean 3rd Qu.    Max.    NA's 
#0.0    11.0    20.5    26.3    33.0   113.0      23 

```

```{r Field.Experiment}
## LOAD LIBRARY AND READ IN DATA
library(survival)
defend <- read.csv("/Users/scott/Desktop/Ceph AZ ET Cleaned for Analyses/field_expt-surv_simp.csv")


## SUBSETTING DATA
defend_s <- defend[ which(defend$hole_size=='S'), ] #Subset data for all small entrance cavities

defend_s_yn <-defend_s[which(defend_s$soldiers=='y'), ] #Subset data for whether cavities have soldiers or not

defend_s0s1 <-defend_s[which(defend_s$s0_s1=='y'), ] #Subset data for only s0 and s1 cavities

defend_s0s6 <-defend_s[which(defend_s$s0_s6=='y'), ] #Subset data for only s0 and s6 cavities

defend_s1s6 <-defend_s[which(defend_s$s1_s6=='y'), ] #Subset data for only s1 and s6 cavities 


## CREATE SURVIVAL OBJECTS
defend_surv <- Surv(defend$week, defend$death) #Survival object for all data

defend_surv_s <- Surv(defend_s$week, defend_s$death) #Survival object for all small-ent data

defend_surv_s0s1 <- Surv(defend_s0s1$week, defend_s0s1$death) #Survival data for all s0 and s1 data

defend_surv_s0s6 <- Surv(defend_s0s6$week, defend_s0s6$death) #Survival data for all s0 and s6 data

defend_surv_s1s6 <- Surv(defend_s1s6$week, defend_s1s6$death) #Survival data for all s1 and s6 data


## SURVIVAL ANALYSES FOR ALL COMBINATIONS

survdiff(defend_surv ~ defend$hole_size, rho=0) #Comparison of small vs. bigs ents. 
                    #N Observed Expected (O-E)^2/E (O-E)^2/V
#defend$hole_size=B 33       33     20.1      8.29      37.4
#defend$hole_size=S 33       20     32.9      5.06      37.4
#Chisq= 37.4  on 1 degrees of freedom, p= 9.47e-10 

survdiff(defend_surv_s ~ defend_s$nest, rho=0) #Comparison for 0, 1, and 6 soldiers.
                  #N Observed Expected (O-E)^2/E (O-E)^2/V
#defend_s$nest=S0 11       11     5.93     4.335     7.256
#defend_s$nest=S1 11        7     8.27     0.195     0.359
#defend_s$nest=S6 11        5     8.80     1.641     3.149 
#Chisq= 7.6  on 2 degrees of freedom, p= 0.0218

survdiff(defend_surv_s0s1 ~ defend_s0s1$nest, rho=0) #Comparison of 0 vs. 1 soldier. 
                     #N Observed Expected (O-E)^2/E (O-E)^2/V
#defend_s0s1$nest=S0 11       11      7.1      2.14       4.6
#defend_s0s1$nest=S1 11        7     10.9      1.39       4.6
#Chisq= 4.6  on 1 degrees of freedom, p= 0.0321 

survdiff(defend_surv_s0s6 ~ defend_s0s6$nest, rho=0) #Comparison of 0 vs. 6 soldier. 
                     #N Observed Expected (O-E)^2/E (O-E)^2/V
#defend_s0s6$nest=S0 11       11     6.52      3.08      6.41
#defend_s0s6$nest=S6 11        5     9.48      2.12      6.41
#Chisq= 6.4  on 1 degrees of freedom, p= 0.0114 

survdiff(defend_surv_s1s6 ~ defend_s1s6$nest, rho=0) #Comparison of 1 vs. 6 soldier. 
                     #N Observed Expected (O-E)^2/E (O-E)^2/V
#defend_s1s6$nest=S1 11        7     5.77     0.262     0.567
#defend_s1s6$nest=S6 11        5     6.23     0.243     0.567
#Chisq= 0.6  on 1 degrees of freedom, p= 0.452 


### Simple survival plot for all three small-ent treatments
plot_s <- survfit((defend_surv_s ~ defend_s$nest), conf.type="none")
plot(plot_s, xlab="Time", ylab="Proportional cavity survival") # Plot with all lines


### Fancy survival plot for all three small-ent treatments
par(pty="s", bty="l", fin=c(4.0, 4.0)) #Set plot space
defend_s0 <- defend[ which(defend$nest=='S0'), ] #subset for s0 data
defend_surv_s0 <- Surv(defend_s0$week, defend_s0$death) #survival object for s0 data
plot_s0 <- survfit((defend_surv_s0 ~ defend_s0$nest), conf.type="none") #create survival curve for s0
defend_s1 <- defend[ which(defend$nest=='S1'), ] #subset for s1 data
defend_surv_s1 <- Surv(defend_s1$week, defend_s1$death) #survival object for s1 data
plot_s1 <- survfit((defend_surv_s1 ~ defend_s1$nest), conf.type="none") #create survival curve for s1
defend_s6 <- defend[ which(defend$nest=='S6'), ] #subset for s6 data
defend_surv_s6 <- Surv(defend_s6$week, defend_s6$death) #survival object for s6 data
plot_s6 <- survfit((defend_surv_s6 ~ defend_s6$nest), conf.type="none") #create survival curve for s6
plot(plot_s6, xlab="Weeks", ylab="Proportion of surviving cavities", mgp=c(3,0.6,0), lty=1, tck=-0.02, cex.axis=0.8, las=1) # Plot with S6 nests
lines(plot_s1, lty=2) # Line for S1 nests
lines(plot_s0, lty=3) # Line for S0 nests
```

```{r Lab.Experiments}

## READ IN DATA
et_sum <- read.csv("/Users/scott/Desktop/Ceph AZ ET Cleaned for Analyses/lab_expt-ET_sum.csv")
et_sum_sizes <-read.csv("/Users/scott/Desktop/Ceph AZ ET Cleaned for Analyses/lab_expt-ET_sum_sizes.csv")
et_sum_sizes_l_no0 <- read.csv("/Users/scott/Desktop/Ceph AZ ET Cleaned for Analyses/lab_expt-ET_sum_sizes-lno0.csv")
et_sum_sizes_s_no0 <- read.csv("/Users/scott/Desktop/Ceph AZ ET Cleaned for Analyses/lab_expt-ET_sum_sizes-sno0.csv")
et_sum_sizes_nt_no0 <- read.csv("/Users/scott/Desktop/Ceph AZ ET Cleaned for Analyses/lab_expt-ET_sum_sizes_nt_no0.csv")
et_sum_sizes_t_no0 <- read.csv("/Users/scott/Desktop/Ceph AZ ET Cleaned for Analyses/lab_expt-ET_sum_sizes_t_no0.csv")
et_sum_td <- read.csv("/Users/scott/Desktop/Ceph AZ ET Cleaned for Analyses/lab_expt-ET_sum_td.csv")
et_o_n <- read.csv("/Users/scott/Documents/Current papers/Ceph AZ Papers/Ceph AZ Ent-Threat Paper/Ceph AZ Ent-Threat Paper Analyses/Ceph AZ ET Cleaned for Analyses/lab_expt-ET_orig_new.csv")
sold_nests_nt <- read.csv("/Users/scott/Dropbox/Current papers/Ceph AZ Papers/Ceph AZ Ent-Threat Paper/Ceph AZ Ent-Threat Paper Analyses/Ceph AZ ET Cleaned for Analyses/lab_expt-sold_nest_nt.csv")
sold_nests_t <- read.csv("/Users/scott/Dropbox/Current papers/Ceph AZ Papers/Ceph AZ Ent-Threat Paper/Ceph AZ Ent-Threat Paper Analyses/Ceph AZ ET Cleaned for Analyses/lab_expt-sold_nest_t.csv")


## CAVITY USE & DEFENSE
### Subset data
et_sum_nt<-(et_sum[et_sum$treatment=="no_threat",])
et_sum_t<-(et_sum[et_sum$treatment=="threat",])

### Analyses of number of cavities occupied - USING ONLY TOTAL NEW NESTS
wilcox.test(et_sum_nt$total_new_nests, et_sum_t$total_new_nests, paired=TRUE) #Total cavity use under threat and no-threat
#V = 22, p-value = 0.1984
var.test(log(et_sum_nt$total_new_nests), log(et_sum_t$total_new_nests))
#F = 0.5592, num df = 11, denom df = 11, p-value = 0.3493
t.test(log(et_sum_nt$total_new_nests), log(et_sum_t$total_new_nests), paired=TRUE)
#t = 1.409, df = 11, p-value = 0.1865


wilcox.test(et_sum_nt$total_new_nests_large, et_sum_nt$total_new_nests_small, paired = TRUE)
#V = 9, p-value = 0.1817
var.test(log(et_sum_nt$total_new_nests_large), log(et_sum_nt$total_new_nests_small))
t.test(log(et_sum_nt$total_new_nests_large), log(et_sum_nt$total_new_nests_small), paired = TRUE)
#t = -1.6085, df = 11, p-value = 0.136

wilcox.test(et_sum_t$total_new_nests_large, et_sum_t$total_new_nests_small, paired = TRUE)
#V = 3.5, p-value = 0.04033
var.test(log(et_sum_t$total_new_nests_large), log(et_sum_t$total_new_nests_small))
t.test(log(et_sum_t$total_new_nests_large), log(et_sum_t$total_new_nests_small), paired = TRUE) #won't run

### Analyses of number of defended cavities
wilcox.test(et_sum_nt$total_sold_nests, et_sum_t$total_sold_nests, paired=TRUE)
#V = 40.5, p-value = 0.02475
var.test(log(et_sum_nt$total_sold_nests), log(et_sum_t$total_sold_nests))
#F = 0.4611, num df = 11, denom df = 11, p-value = 0.2149
t.test(log(et_sum_nt$total_sold_nests), log(et_sum_t$total_sold_nests), paired=TRUE)
#t = 2.789, df = 11, p-value = 0.01762


et_sum_nt<-(et_sum[et_sum$treatment=="no_threat",])
wilcox.test(et_sum_nt$total_sold_nests_large, et_sum_nt$total_sold_nests_small, paired = TRUE)
#V = 33.5, p-value = 0.2074
var.test(log(et_sum_nt$total_sold_nests_large), log(et_sum_nt$total_sold_nests_small))
#F = 1.997, num df = 11, denom df = 9, p-value = 0.3086
t.test(log(et_sum_nt$total_sold_nests_large), log(et_sum_nt$total_sold_nests_small), paired = TRUE)



et_sum_t<-(et_sum[et_sum$treatment=="threat",])
wilcox.test(et_sum_t$total_sold_nests_large, et_sum_t$total_sold_nests_small, paired = TRUE)
#V = 26.5, p-value = 0.9578

### Figure for total defended cavities under no-threat and threat.
library(lattice)
dotplot(jitter(total_new_nests,0) ~ treatment, group=colony, data=et_sum, col="black", type=c("b"), ylab="Total new occupied nests", xlab="Threat context", aspect = 3/1.1, ylim=c(0.8,8.2)) # remove "col" argument to default to colored bars.

library(lattice)
dotplot(jitter(total_sold_nests,0.3) ~ treatment, group=colony, data=et_sum, col="black", type=c("b"), ylab="Total new defended nests", xlab="Threat context", aspect = 3/1.1, ylim=c(0.8,8.2)) # remove "col" argument to default to colored bars.

### Figure for total defended large and small ent nests under no-threat
library(lattice)
dotplot(jitter(total_sold_nests,0.3) ~ ent, group=colony, data=sold_nests_nt, col="black", type=c("b"), ylab="New soldier-defended nests", xlab="Entrance size", aspect = 3/1.1, ylim=c(-0.2,4.2)) # remove "col" argument to default to colored bars.

### Figure for total defended large and small ent nests under threat
library(lattice)
dotplot(jitter(total_sold_nests,0.3) ~ ent, group=colony, data=sold_nests_t, col="black", type=c("b"), ylab="New soldier-defended nests", xlab="Entrance size", aspect = 3/1.1, ylim=c(-0.2,4.2)) # remove "col" argument to default to colored bars.

```


```{r Level.Defense.in.New.Defended.Cavities}

### Subset data
et_o_n_nt <- (et_o_n[et_o_n$treatment=="no_threat",])
et_o_n_t <- (et_o_n[et_o_n$treatment=="threat",])
et_sum_sizes_l<-(et_sum_sizes[et_sum_sizes$ent=="l",])
et_sum_sizes_s<-(et_sum_sizes[et_sum_sizes$ent=="s",])
et_sum_nt<-(et_sum[et_sum$treatment=="no_threat",])
et_sum_t<-(et_sum[et_sum$treatment=="threat",])

### Mean level of defense in original versus new cavities
var.test(log(et_o_n_nt$mean_solds_o), log(et_o_n_nt$mean_solds_n)) #Test equal variance of log transformed no_threat data
# F = 0.1954, num df = 11, denom df = 11, p-value = 0.01169 SO, t-test not valid.
wilcox.test(et_o_n_nt$mean_solds_o, et_o_n_nt$mean_solds_n, paired = TRUE) # Paired test for diff between mean level of defense in original and new cavities for no_threat treatement
# V = 73, p-value = 0.004883

wilcox.test(et_o_n_t$mean_solds_o, et_o_n_t$mean_solds_n, paired = TRUE) # Paired test for diff between mean level of defense in original and new cavities for threat treatement
# V = 66, p-value = 0.00384

### Level of defense in large and small cavities under no-threat & threat
et_sum_nt_no0 <- (et_sum_nt[et_sum_nt$av_def_large>0.0 & et_sum_nt$av_def_small>0.0,]) #subset for colonies that defended at least one large and one small colony under no-threat conditions
wilcox.test(et_sum_nt_no0$av_def_large, et_sum_nt_no0$av_def_small, paired = TRUE) #Test for all subsetted colonies defending at least one large and one small under no-threat
#V = 36, p-value = 0.01415

var.test(log(et_sum_nt_no0$av_def_large), log(et_sum_nt_no0$av_def_small)) #Test for all subsetted colonies defending at least one large and one small under no-threat
t.test(log(et_sum_nt_no0$av_def_large), log(et_sum_nt_no0$av_def_small), paired = TRUE) #Test for all subsetted colonies defending at least one large and one small under no-threat
#t = 3.6446, df = 9, p-value = 0.005363

et_sum_t_no0 <- (et_sum_t[et_sum_t$av_def_large>0.0 & et_sum_t$av_def_small>0.0,]) #subset for colonies that defended at least one large and one small colony under threat conditions
wilcox.test(et_sum_t_no0$av_def_large, et_sum_t_no0$av_def_small, paired = TRUE) #Test for all subsetted colonies defending at least one large and one small under threat
#V = 16, p-value = 0.2945

var.test(log(et_sum_t_no0$av_def_large), log(et_sum_t_no0$av_def_small)) #Test for all subsetted colonies defending at least one large and one small under no-threat
t.test(log(et_sum_t_no0$av_def_large), log(et_sum_t_no0$av_def_small), paired = TRUE) #Test for all subsetted colonies defending at least one large and one small under no-threat
#t = 0.9471, df = 6, p-value = 0.3802


### Figure for level of defense in small and large cavities in two contexts
library(lattice)
dotplot(jitter(av_def,0) ~ ent, group=colony, data= et_sum_sizes_nt_no0, col="black", type=c("b"), ylab="Mean soldiers per cavity", xlab="Entrance size", aspect = 3/1.1, ylim=c(0.6,8.4)) #Figure for level of defense in large and small ent cavities under no-threat for only colonies that defended at least one cavity of both ent sizes. Height on quartz window overridden to 3.8 inches

library(lattice)
dotplot(jitter(av_def,0) ~ ent, group=colony, data= et_sum_sizes_t_no0, col="black", type=c("b"), ylab="Mean soldiers per cavity", xlab="Entrance size", aspect = 3/1.1, ylim=c(0.6,8.4)) #Figure for level of defense in large and small ent cavities under threat for only colonies that defended at least one cavity of both ent sizes. Height on quartz window overridden to 3.8 inches


```

```{r Total.Soldier.Deployment}

### Total deployment under threat and no threat
wilcox.test(et_sum$total_sold_dep ~ et_sum$treatment, paired = TRUE)
#V = 68.5, p-value = 0.02228
#This uses the wilcox formula argument, with the data for each colony in sucessive rows, and the same consistent treatment order. Other arangements are incorrect.

wilcox.test(et_sum_td$total_sold_dep_nt, et_sum_td$total_sold_dep_t, paired=TRUE)
#V = 68.5, p-value = 0.02228
#This uses the wilcoxon arrangement of data for each treatment split between differnt vectors, with the data in teh same row treated as the pairs. This verifies the result uding the formula argument.

var.test(log(et_sum_td$total_sold_dep_nt), log(et_sum_td$total_sold_dep_t))
#F = 0.4445, num df = 11, denom df = 11, p-value = 0.1944
t.test(log(et_sum_td$total_sold_dep_nt), log(et_sum_td$total_sold_dep_t), paired=TRUE)
#t = 2.9789, df = 11, p-value = 0.01254



### Proportional total deployment under threat and no threat
wilcox.test(et_sum_td$prop_sold_dep_nt, et_sum_td$prop_sold_dep_t, paired=TRUE) #Proportional soldier deployment
#V = 55.5, p-value = 0.05035 

var.test(log(et_sum_td$prop_sold_dep_nt), log(et_sum_td$prop_sold_dep_t))
#F = 0.3503, num df = 11, denom df = 11, p-value = 0.09601
t.test(log(et_sum_td$prop_sold_dep_nt), log(et_sum_td$prop_sold_dep_t), paired=TRUE) #Proportional soldier deployment
#t = 2.6764, df = 11, p-value = 0.02155

### Regression lines for total and deployed soldiers under no-threat
sd_on_s_nt <- lm(log(total_sold_dep) ~ log(sold_avail), data=et_sum_nt)
summary(sd_on_s_nt)
#Residual standard error: 0.4597 on 10 degrees of freedom
#Multiple R-squared:  0.5295,	Adjusted R-squared:  0.4825 
#F-statistic: 11.26 on 1 and 10 DF,  p-value: 0.007304


x<-log(et_sum_nt$sold_avail) #Sig test slope diff. from 1, using this manual code block
y<-log(et_sum_nt$total_sold_dep)
model<-lm(y~x)
es<-resid(model)	# the residuals of the defined y~x model
b1<-coef(model)[["x"]] # the x part of the coefficients
s<-sqrt( sum( es^2 ) / (10) ) # 10 in bracket is n-2 d.f.
SE<-s/sqrt(sum((x-mean(x))^2))
t<-(b1-(1))/SE	# 1 in inner brackets is the slope value for comparison
2*pt(abs(t), 10, lower.tail=FALSE)	# abs() makes the t-value absolute so p-calcs are not affected by returned neg. t-values, 2nd value [10] is n-2 d.f., lower.tail=FALSE gives upper tail (one-tail) P-value, 2* multiples 1-tail result to give 2-tail P-value out

#0.9762876 Outputted p-value, so here slope is NOT sig. diff. from 1

(b1-(1))/SE #copied and pasted from within above code to give t-value for reporting. Can double check outputted P-value by comparing this t-value against tables

#0.03047536 Outputted t-value


### Regression lines for total and deployed soldiers under threat
sd_on_s_t <- lm(log(total_sold_dep) ~ log(sold_avail), data=et_sum_t)
summary(sd_on_s_t)
#Residual standard error: 0.773 on 10 degrees of freedom
#Multiple R-squared:  0.4088,	Adjusted R-squared:  0.3497 
#F-statistic: 6.914 on 1 and 10 DF,  p-value: 0.02518

x<-log(et_sum_t$sold_avail) #Sig test slope diff. from 1, using this manual code block
y<-log(et_sum_t$total_sold_dep)
model<-lm(y~x)
es<-resid(model)	# the residuals of the defined y~x model
b1<-coef(model)[["x"]] # the x part of the coefficients
s<-sqrt( sum( es^2 ) / (10) ) # 10 in bracket is n-2 d.f.
SE<-s/sqrt(sum((x-mean(x))^2))
t<-(b1-(1))/SE	# 1 in inner brackets is the slope value for comparison
2*pt(abs(t), 10, lower.tail=FALSE)	# abs() makes the t-value absolute so p-calcs are not affected by returned neg. t-values, 2nd value [10] is n-2 d.f., lower.tail=FALSE gives upper tail (one-tail) P-value, 2* multiples 1-tail result to give 2-tail P-value out

#0.6362349 Outputted p-value, so here slope is NOT sig. diff. from 1

(b1-(1))/SE # copied and pasted from within above code to give t-value for reporting. Can double check outputted P-value by comparing this t-value against tables

#0.4877624 Outputted t-value


### Figure of total soldier deployment on soldier availability
par(pty="s", fin=c(4.0, 4.0))
with(et_sum_nt, plot(log(sold_avail), log(total_sold_dep), pch=21, bg="gray80", xlab="", ylab="", xaxt="n", yaxt="n", bty="l", xlim=c(log(7),log(50)), ylim=c(log(1),log(30))))
abline(lm(log(total_sold_dep) ~ log(sold_avail), data=et_sum_nt), lwd=1.25)

xtemptck <- c(7,8,9,10,20,30,40,50)
ytemptck <- c(1,2,3,4,5,6,7,8,9,10,20,30)
axis(1, at=log(c(7,10,50)), label=c(7,10,50), mgp=c(2,0.3,0), lwd=0, cex.axis=0.8)
axis(1, at=log(xtemptck), mgp=c(2,0.3,0), tck=-0.02, label=F, lwd=0, lwd.ticks=1)
axis(2, at=log(c(2,10,30)), label=c(2,10,30), mgp=c(3,0.6,0), lwd=0, cex.axis=0.8, las=1)
axis(2, at=log(ytemptck), mgp=c(3,0.6,0), tck=-0.02, label=F, lwd=0, lwd.ticks=1)
mtext("Available soldiers", side=1, line=2)
mtext("Soldiers deployed to new cavities", side=2, line=2.6)

with(data=et_sum_t, (points(log(sold_avail), log(total_sold_dep), pch=23, cex=1, bg="white")))
abline(lm(log(total_sold_dep) ~ log(sold_avail), data=et_sum_t), lty=5, lwd=1.25, col="black") #Codes for cavity area points

abline(a=-1.0192, b=1, lty=3, col="black", lwd=0.75) #Code for slope = 1 line, using intercept value for the non-threatened relationship. Optional to include

abline(a=-2.1771, b=1, lty=3, col="grey50", lwd=0.75) #Code for slope = 1 line, using intercept value for the threat relationship. Optional to include


```


# References 