---
title: "Reproducing Powell et Al. 2017"
author: "Fiona Lightbody"
date: "9/28/2020"
output:
  pdf_document: default
bibliography: Powell.bib
---

#Reproducing code from 
#[@Powell:2017dd] 



#COMPLETED: loaded in data and packages 
```{r setup, include=TRUE}
rm(list=ls())

library(survival)
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```
#package 'survival' was built under R version 3.6.2 and was downloaded in the binary format, not the source version

```{r data_input, include=TRUE}
Collection_data <- read_csv("~/Google Drive/AA Graduate /Data and Software Tools EBIO6660/data/Cephalotes_rohweri_collection_data.csv") 
Field_expt <- read_csv("~/Google Drive/AA Graduate /Data and Software Tools EBIO6660/data/Cephalotes_rohweri_field_expt.csv")

Lab_expt <- read_csv("~/Google Drive/AA Graduate /Data and Software Tools EBIO6660/data/Cephalotes_rohweri_lab_expt.csv")

```
#data was readily available by the author in csv format. So far no metadata or code has been located for this paper. 

#STILL WORKING ON IT: Next I will work with the data to generate summarizing graphics and work on the first boxplot which I seek to reproduce. Next I will familiarize myself with the survival package in order to generate the survivorship curve. 

### PROGRESS REPORT OCT 25 
##STUCK: need to understand difference between col character and col double: running the above data into R gets this in response (below), likely because Powell used solely R (not R Studio) to peform his analysis. Code has not yet been receieved, but contact was made. 
#Parsed with column specification: 
cols(
  colony = col_character(),
  nest_no = col_double(),
  workers = col_double(),
  soldiers = col_double(),
  ent_area_mm = col_double()
)
Parsed with column specification:
cols(
  tree = col_character(),
  entrance_size = col_character(),
  nest_pop = col_character(),
  week_death = col_character()
)
Parsed with column specification:
cols(
  colony = col_character(),
  treatment = col_character(),
  position = col_double(),
  entrance = col_character(),
  treatment_phase = col_character(),
  workers = col_character(),
  soldiers = col_double(),
  eggs = col_character(),
  larvae = col_character(),
  pupae = col_character()
)